Paper_Figure

### 2024-08-11 README.Rmd
package_refine

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LMD

@@

The goal of LMD is to ...

@@

You can install the released version of LMD from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("LMD")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ruiqi0130/LocalMarkerDetector")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(LMD)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures",
  out.width = "100%"
)
```

# Localized Marker Detector

@@

Localized Marker Detector (LMD) is a computational framework designed for the identification of gene expression markers localized to specific cell populations within single-cell RNA sequencing data. The major workflow of LMD comprises the following three main steps:

* Step1. Constructing a cell-cell affinity graph
* Step2. Diffusing the gene expression value across the cell graph
* Step3. Assigning a score to each gene based on the dynamics of its diffusion process
* Optional Downstream tasks
  * Identifying gene modules and characterizing functional cell groups
  * Cross-sample comparison

```{r pressure, echo=FALSE, out.width="50%", out.height="auto"}
knitr::include_graphics("./man/figures/LMD_workflow.png")
```

@@

LMD can be installed in R as follows:

``` r
install.packages("devtools")
devtools::install_github("ruiqi0130/LocalizedMarkerDetector")

library("LocalizedMarkerDetector")
```

## Example tutorial
Please check [LMD tutorial](https://ruiqi0130.github.io/LocalizedMarkerDetector/articles/).

## References
References of LMD functions can be found [here](https://ruiqi0130.github.io/LocalizedMarkerDetector/reference/index.html).

<!-- Data used in this tutorial can be downloaded from [Tabula Muris](https://figshare.com/ndownloader/files/13092380). -->
